Setup:
```{r setup, include<-FALSE}
knitr::opts_chunk$set(echo <- TRUE)
```

# Global.R Setup
```{r}
# R Packages
packages = c('shiny', 
            'shinydashboard', 
            'shinyWidgets', 
            'DT', 
            'leaflet',
            'tidyverse',
            'knitr',
            'stringr',
            'httr',
            'geojsonio', 
            'sp', 
            'dplyr', 
            'SpatialAcc', 
            'rgeos', 
            'spdplyr', 
            'KernSmooth', 
            'raster',
            'reshape2', 
            'sf',
            'rgdal',
            'spdep',
            'tmap'
            )

for (p in packages){
    if(!require(p, character.only = T)){ 
        install.packages(p)
    }
    library(p,character.only = T) 
}

memory.limit(size=56000)


# Folder Paths
dp_a_prefix = "../data/aspatial/" 
dp_j_prefix = "../data/geojson/" 
dp_m_prefix = "../data/distancematrix/" 
dp_h_prefix = "../data/hansen/" 
dp_s_prefix = "../data/sam/" 

# Data Paths
dp_a_jc = paste(dp_a_prefix, "jc.csv", sep="")
dp_a_zip = paste(dp_a_prefix, "sg_zipcode_mapper.csv", sep="")

# Data variables
jc_data <- read.csv(dp_a_jc)
zip_data <- read.csv(dp_a_zip)

# Data Wrangling
jc_data$POSTAL <- as.numeric(jc_data$POSTAL)
jc <- jc_data%>% 
    dplyr::select("SCHOOL"='SEARCHVAL', 'POSTAL', 'LATITUDE', 'LONGITUDE', 'X', 'Y', 'ROAD_NAME','ADDRESS', 'REGION')

hdb <- zip_data%>%
    dplyr::select('ADDRESS' = 'address', 'POSTAL'="postal", 'LATITUDE' = 'latitude', 'LONGITUDE' = 'longtitude', 'ROAD_NAME' = 'road_name')


# CRS
crsobj = CRS("+init=EPSG:3414")

coordinates(jc)<-~LONGITUDE+LATITUDE
proj4string(jc) = crsobj

coordinates(hdb)<-~LONGITUDE+LATITUDE
proj4string(hdb) = crsobj
```


# Isochrone generation for all JC 

function to get geojson
```{r}
library(httr)
get_geojson<-function(lat,lng,filename){

    current <- GET(
        "http://localhost:8080/otp/routers/current/isochrone",
        query = list(
            fromPlace = paste(lat,lng,sep = ","), # latlong of place
            mode = "WALK,TRANSIT", # modes we want the route planner to use
            date = "05-11-2020",
            time= "07:00am",
            maxWalkDistance = 1600, # in metres
            walkReluctance = 5,
            minTransferTime = 60, # in secs
            cutoffSec = 900,
            cutoffSec = 1800,
            cutoffSec = 2700,
            cutoffSec = 3600
        )
    )
    
    current <- content(current, as = "text", encoding = "UTF-8")
    write(current, file = paste0(dp_j_prefix, lsch, '.geojson'))
}
```


saves the isochrone generation for each JC as .rds in data/geojson/
Only run this code chunk if you want to generate the .rds files 
```{r}
for (i in 1:19){
    lsch = jc@data[i,'SCHOOL']
    print(lsch)
    lat = jc@coords[i,2]
    long = jc@coords[i,1]
    print(lat)
    print(long)
    
    get_geojson(lat, long, lsch)
    sp = geojsonio::geojson_read(paste0(dp_j_prefix, lsch, '.geojson'), what = "sp")
    proj4string(sp) = proj4string(hdb)
    res = colSums(gContains(sp, hdb, byid = TRUE))
    print(res)
    res = tbl_df(res)
    colnames(res) = 'blocks'
    sp@data = bind_cols(sp@data, res)
    saveRDS(sp, file = paste0(dp_j_prefix, lsch, '.rds'))
}
```


# Generate distance matrix
Get_dist function to get the data information of a trip with the fastest route.
generate_dist function to generate the distance matrix and duration from all the residential data to each school.
```{r}
#Getting the data of a trip
get_dist = function(fromLat, fromLong, toLat, toLong){
        current <- GET(
            "http://localhost:8080/otp/routers/default/plan",
            query = list(
                fromPlace = paste(fromLat,fromLong,sep = ","), # latlong of place
                toPlace = paste(toLat,toLong,sep = ","),
                mode = "WALK,TRANSIT", # modes we want the route planner to use
                date = "05-11-2020",
                time= "07:00am",
                maxWalkDistance = 1600, # in metres
                cutoffSec = 900,
                cutoffSec = 1800,
                cutoffSec = 2700,
                cutoffSec = 3600
            )
        )

        if (length(content(current)[["plan"]][["itineraries"]][[1]]) == 0){
            return(NULL)
        }else{
            return(content(current)[["plan"]][["itineraries"]][[1]])
        }
}
#Generating the dist and duration from all residential HDB and storing it for each school
generate_dist <-function(hdb, destLat, destLong, schName){
    result = data.frame(matrix(ncol = 6, nrow= 0))
    colnames(result) = c('address', 'destination', 'latitude', 'longitude', 'duration', 'distance')
    
    for(i in 1: length(hdb@coords[,1])){
        lat = as.double(hdb@coords[i,]['LATITUDE'])
        long = as.double(hdb@coords[i,]['LONGITUDE'])
        address = hdb@data[i,]$ADDRESS
            info = get_dist(lat, long, destLat, destLong)
            if (is.null(info)){
                next()
            }
            total = 0
            for (j in 1:length(info$legs)){
                total = total + info$legs[[j]]$distance
            }
            
            dist = total/1000 #convert to km
            dur = info$duration/60
            result[nrow(result)+1,] = list(address, schName, lat, long, dur, dist)
            print(result)
            
    }
    return(result)
}
```

Run this code to generate the .rds files (distancematrix)
```{r}
    x=1 #input x
    schName = jc@data[x,"SCHOOL"]
    print(schName)
    schLat = jc@coords[x,2]
    schLong =    jc@coords[x,1]
    result=generate_dist(hdb, schLat, schLong, schName)
    saveRDS(result, file = paste0(dp_m_prefix, schName, '.rds'))
```


# Measure accessibility with Hansen

Hansen function
```{r}
apply_hansen = function(res){
    result = res %>% mutate(demand =100)
    durationMatrix = result %>% dplyr::select('duration')
    acc_hansen <- data.frame(ac(result$demand,
                                                            c(10), 
                                                            durationMatrix,
                                                            power = 2, 
                                                            family = "Hansen"))
    result_duration = result
    result_duration$durationHansen = acc_hansen[,1]
    result_duration$durationHansen[is.na(result_duration$durationHansen)] = 0
    
    
    distanceMatrix = result %>% dplyr::select('distance')
    acc_hansen <- data.frame(ac(result$demand,
                                                            c(10), 
                                                            distanceMatrix,
                                                            power =2, 
                                                            family = "Hansen"))
    result_final = result_duration
    result_final$distanceHansen = acc_hansen[,1]
    result_final$distanceHansen[is.na(result_final$distanceHansen)] = 0
    return (result_final)
}
```

Hansen Generation for each school distance matrix
```{r}
for (x in 1:19){
    schName = jc@data[x,'SCHOOL']
    print(schName)
    res = readRDS(paste0(dp_m_prefix,schName,'.rds'))
    
    result_acc = apply_hansen(res)
    
    result_acc<- result_acc%>%
        mutate(durationHansen=durationHansen*10000) # for legend as it is too small to be meaningful
    
    result_acc$address <- rapportools::tocamel(tolower(result_acc$address), upper=TRUE, sep=" ")
    result_acc <- result_acc %>% 
        mutate(hansenDistLabel = paste(
                "Distance Hansen Acessibility:","<b>",round(distanceHansen,4),
                "</b><br/>","Address: ",address,
                "</br>Distance to School: ","<b>",round(distance,4),"<b/> Kilometres"), 
            hansenDuraLabel = paste(
                "Duration Hansen Acessibility: ","<b>",round(durationHansen,4),
                "</b><br/>Address:",address,
                "</br>Duration to School: ","<b>",round(duration,4),"</b> Minutes"))
    
    result_acc_sf <- st_as_sf(result_acc, 
    coords = c('longitude', 'latitude'),
    crs = "+init=epsg:3414")

    result_acc_sp <- sf:::as_Spatial(result_acc_sf)
    
    saveRDS(result_acc_sp, paste0(dp_h_prefix,schName,'.rds'))
}
```

# Measure accessibility with SAM
SAM function
```{r}
apply_sam = function(res){
    result = res %>% mutate(demand =100)
    durationMatrix = result %>% dplyr::select('duration')
    acc_sam <- data.frame(ac(result$demand,
                                                            c(10), 
                                                            durationMatrix,
                                                            power = 2, 
                                                            family = "SAM"))
    result_duration = result
    result_duration$durationSam = acc_sam[,1]
    result_duration$durationSam[is.na(result_duration$durationSam)] = 0
    
    
    distanceMatrix = result %>% dplyr::select('distance')
    acc_sam <- data.frame(ac(result$demand,
                                                            c(10), 
                                                            distanceMatrix,
                                                            power =2, 
                                                            family = "SAM"))
    result_final = result_duration
    result_final$distanceSam = acc_sam[,1]
    result_final$distanceSam[is.na(result_final$distanceSam)] = 0
    return (result_final)
}
```

SAM Generation for each school distance matrix
```{r}
for (x in 1:19){
    schName = jc@data[x,'SCHOOL']
    print(schName)
    res = readRDS(paste0(dp_m_prefix,schName,'.rds'))

    result_acc = apply_sam(res)
    
    result_acc<- result_acc%>%
        mutate(durationSam=durationSam*1000) # for legend as it is too small to be meaningful
    
    result_acc$address <- rapportools::tocamel(tolower(result_acc$address), upper=TRUE, sep=" ")
    result_acc <- result_acc %>% 
        mutate(samDistLabel = paste(
                "Distance SAM Acessibility:","<b>",round(distanceSam,4),
                "</b><br/>","Address: ",address,
                "</br>Distance to School: ","<b>",round(distance,4),"<b/> Kilometres"), 
            samDuraLabel = paste(
                "Duration SAM Acessibility: ","<b>",round(durationSam,4),
                "</b><br/>Address:",address,
                "</br>Duration to School: ","<b>",round(duration,4),"</b> Minutes"))

    result_acc_sf <- st_as_sf(result_acc, 
    coords = c('longitude', 'latitude'),
    crs = "+init=epsg:3414")

    result_acc_sp <- sf:::as_Spatial(result_acc_sf)
    
    saveRDS(result_acc_sp, paste0(dp_s_prefix,schName,'.rds'))
}
```
