---
title: Merge'R'Us; Visualising Accessibility of Junior Colleges
author:
  - name: Constance Tan
    affil: 1
  - name: Fiona Wee 
    affil: 1
  - name: Jasmine Toh
    affil: 1
affiliation:
  - num: 1
    address: School of Information Systems, Singapore Management University
column_numbers: 3
logoright_name: https&#58;//logos-download.com/wp-content/uploads/2016/12/Singapore_Management_University_logo_SMU.png
logoleft_name: https&#58;//brave-bhaskara-fc4519.netlify.app/img/logo.png
output: 
  posterdown::posterdown_pdf:
    self_contained: false
bibliography: packages.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Introduction

The Ministry of Education (MOE) of Singapore has called for the amalgamation and relocation of some schools, including primary schools, secondary schools as well as junior colleges.

This is reported to be due to the fall in birth rate that led to lesser demand for education services and changes in geographical distribution of students. As a result, there is an adverse impact on accessibility for some students.

## **Project Objectives**
In our project, we will build an application to investigate the effect of the new locations of the affected schools on the spatial accessibility to Junior College (JC) students.

Mainly, we wish to create an isochrone map and visualise the modelling results of Hansen accessibility model and Spatial Accessibility Measure.

We will then analyse and interpret the output. We are also interested in identifying the affected residential areas which require more attention and comment on potential amalgamation by doing evaluations and stating the challenges.

## **Project Motivation**

Many families have been impacted in terms of accessibility due to the policy, with some moving houses or being inconvenienced. We wish to explore the extent of this as well as identify the areas impacted. Did the decisions meet its aim, or did it do more harm than good? We are curious about this, and regardless, if any area was impacted adversely, it would be good for measures to be implemented by the government to assist the families affected.

While the initial announcement was a few years back, this situation remains prevalent. There are still future plans for relocation, for example Yusof Ishak Secondary School from an area where demand for school places is falling to Punggol in 2021 to meet the growing demand [@relocation]. While this is grounded, we wonder about the sustainability of moving schools everytime the demand falls. As the downward trend in Singapore's population growth continues, there might be more of such cases to come, which is a cause for concern.

At the same time, the rather recent lavish national expenditure on the building of the new Eunoia JC raised many eyebrows. Many questioned if the move was called for in light of the closures and mergers of the other schools [@commentary], and this is an interesting issue that we can look into on the side. 

Moreover, this topic is close to home as we have members whose JC was merged. Hence, we wish to visualise the and analyse the impact, and perhaps allow insight to be derived on the ideal locations of schools. 


# Methods


# Results

You can reference tables like so: Table \@ref(tab:mytable). 

```{r mytable, out.width='80%'}
knitr::kable(iris[1:10, 1:4], caption = 'Table caption.',align = 'c',"html")
```

Or with figures: Figure \@ref(fig:standard-plot), or Figure \@ref(fig:morefigs).

```{r standard-plot, out.width='80%', fig.align='center', fig.cap='Great figure!', fig.height=5}
plot(mtcars[1:2])
```

```{r morefigs, out.width='80%', echo=TRUE, fig.cap='Amazing, right?!', fig.height=5}
data <- iris

plot(x = data$Sepal.Length, 
     y = data$Sepal.Width, 
     col = data$Species,
     pch = 19, 
     xlab = "Sepal Length (cm)",
     ylab = "Sepal Width (cm)")

```

# Next Steps


# Conclusion

```{r, include=FALSE}
knitr::write_bib(c('knitr','rmarkdown','posterdown','pagedown'), 'packages.bib')
```

# References


---
references:
- id: relocation
  title: MOE to relocate Yusof Ishak Secondary from Bukit Batok to Punggol
  author:
  - family: Chia
    given: Lianne
  issued:
    year: 2018
  URL: https://www.channelnewsasia.com/news/singapore/yusof-ishak-secondary-bukit-batok-punggol-move-moe-10716654
- id: commentary
  title: Look beyond state-of-the-art campuses for what matters in education
  author:
  - family: Tee
    given: Karen
  issued:
    year: 2020
  URL: https://www.channelnewsasia.com/news/commentary/eunoia-junior-college-new-campus-singapore-moe-budget-elitism-12249726
- id: burp
  title: Balancing Urban Residential Plannings (BURP), Visualising the Public Schools Accessibility to Residential Housings.
  author: 
  - family: Tan
    given: Peng Chong
  - family: Brendo
    given: Austin
  - family: Goh
    given: Rebecca
  issued:
    year: 2019
- id: sas
  title: Is there a Space for SAS® Viya® in Healthcare?
  author:
  - family: Lim
    given: Evelyn
  issued:
    year: 2019
- id: kernel
  title: An extended kernel density two-step floating catchment area method to analyze access to health care 
  author:
  - family: Polzin
    given: Pierre
  - family: Borges
    given: José
  - family: Coelho
    given: António
  issued:
    year: 2014
  URL: https://journals-sagepub-com.libproxy.smu.edu.sg/doi/pdf/10.1068/b120050p
...
